### 2020-02-19 report/05-stability.Rmd
Add SEM with bbb and TSR
bbb = stable station
TSR: total species richness

# Compute SEMs
sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

@@

- Main results:
  - Richness destabilizes communities 
  - 
  - Trophic level decreased CV but increase species synchrony!
  - Connectance!

```{r sensitivity, fig.dim = c(14, 7), fig.cap = "Sensivity analysis with different dataset"}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
sem_l_data <- map(list(full = op_analysis, wo_holes = op_analysis_wo_holes, ov = op_analysis_ov),
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    dest_dir = mypath("data", "species"))
)

@@

@@

prod_sem <- compute_prod_sem(.data = sem_data)

>>>>

# Compute SEMs
sem <- compute_stab_sem_rich_beta(.data = sem_data,
  random_effect = as.formula("~1|basin"))

@@

```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

#library(future)
#plan(multiprocess)
sem_sensivity_data <- list(full = op_analysis, wo_holes = op_analysis_wo_holes, bbb = op_analysis_bbb)
sem_l_data <- furrr::future_map(sem_sensivity_data,
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    sem_fun = compute_stab_sem_rich_beta,
    dest_dir = mypath("data", "species"))
)

@@

```{r, fig.dim = c(10, 5)}
p_sensitivity_stab_sem <- map(sem_l_data, ggpiecewisesem)
p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
plot_grid(plotlist = p_sensitivity_stab_sem)
```
```{r}
p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
  group_by(station) %>%
  slice(1) %>%
  ggplot(aes(x = protocol_type)) + 
  geom_histogram(stat ="count") +
  labs(title = "Station bbb")

p_op_analysis_protocol <- op_analysis %>%
  group_by(station) %>%
  slice(1) %>%
  ggplot(aes(x = protocol_type)) + 
  geom_histogram(stat ="count") +
  labs(title = "All stations")
plot_grid(p_op_analysis_protocol_bbb, p_op_analysis_protocol, ncol = 2)
```

```{r, eval = FALSE}
bootstrap_bbb <- map(seq(1,10),
  function(x) {

    sampled_st <- map(c(complete = "complete", partial = "partial"), function (y) {
      st_id <- unique(op_analysis_bbb[op_analysis_bbb$protocol_type == y,
	]$station)
      sample(x = st_id, size = 20, replace = FALSE)
    })

    op_analysis_bbb %>%
      filter(station %in% unlist(sampled_st))
  }
)
names(bootstrap_bbb) <- letters[1:10]

bootstrap_sem <- map(c(bootstrap_bbb, list(full = op_analysis)),
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    sem_fun = compute_stab_sem_rich_beta,
    dest_dir = mypath("data", "species"))
)

sem_results <- map(bootstrap_sem,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

#### CV by basin

```{r}
st_basin %<>%
  mutate(basin = str_replace_all(basin, "RHIN|MEUSE", "RHIN MEUSE"))
sync_basin <- compute_synchrony_over_basin(com = community_analysis, basin = st_basin, .op = op_analysis)
sync_basin %>%
  filter(!is.na(basin)) %>%
  filter(!basin %in% c("ESCAUT SOMME", "MEUSE", "RHIN")) %>%
  ggplot(aes(x = richness_tot, y = 1/ cv_com, label = basin)) +
  geom_point() +
  geom_text(hjust = 0, nudge_x = 0.05) +
  labs(
    x = "Total richness", y = "Biomass stability",
    title = "Basin scale",
    caption = "Average biomass by species by year and by basin was taken to
    compute CV."
  )
```

@@

prod_sem <- compute_prod_sem_rich_beta(.data = sem_data)
